Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-10 paper.qmd
Updated Figure 9b (b1)

tr_from_to_df_two_curvy <- inner_join(
  tr_from_to_df_two_curvy, distance_df_small_edges_two_curvy,
  by = c("from", "to"))

@@

# Define bin width and starting point
bin_width <- hb_obj_two_curvy$a1
start_point <- bin_width/2

@@

tr_from_to_df_two_curvy3 <- inner_join(
  tr_from_to_df_two_curvy2, distance_df_small_edges_two_curvy2,
  by = c("from", "to"))

tr_from_to_df_two_curvy4 <- inner_join(
  tr_from_to_df_two_curvy2, distance_df_small_edges_two_curvy3,
  by = c("from", "to"))

>>>>

bin_width <- hb_obj_two_curvy$a1

####With diff benchmark values

tr_from_to_df_two_curvy4 <- inner_join(
  tr_from_to_df_two_curvy, distance_df_small_edges_two_curvy3,
  by = c("from", "to"))

tr_from_to_df_two_curvy3 <- inner_join(
  tr_from_to_df_two_curvy, distance_df_small_edges_two_curvy2,
  by = c("from", "to"))

## Computed benchmark value
tr_from_to_df_two_curvy <- inner_join(
  tr_from_to_df_two_curvy, distance_df_small_edges_two_curvy,
  by = c("from", "to"))

@@

# Define bin width and starting point
start_point <- bin_width/2

@@
